---
title: "EDS221 Day 7 Sessions"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(palmerpenguins)
library(datapasta)
```

### Data wrangling refresher

#1) Starting from penguins, write a single piped sequence in which you:

-   Only include penguins at Dream and Biscoe Islands

-   Remove the year and sex variables

-   Add a new column body_mass_kg with penguin mass converted from g to kg

-   Rename island variable to location

```{r}
first_wrangle <- penguins %>% 
  filter(island %in% c("Dream", "Biscoe")) %>% 
  dplyr::select(-year, -sex) %>% 
  mutate(body_mass_kg = body_mass_g / 1000) %>% 
  rename(location = island)
```

Starting from penguins, write a single piped sequence to:

-   Limit to Adelie penguins

-   Remove any observations where flipper_length_mm is NA (!is.na() or drop_na)

-   Group the data by sex

-   Create a summary table that contains the mean, st dev and sample size of flipper length for male and female Adelie penguins

```{r}
second_wrangle <- penguins %>% 
  filter(species == "Adelie") %>% 
  drop_na(flipper_length_mm) %>% 
  group_by(sex) %>% 
  summarize(mean_flipper_length = mean(flipper_length_mm),
            sd_flipper_length = sd(flipper_length_mm))
  
```

```{r}
penguins %>% 
  group_by(species, island, sex) %>% 
  summarize(sample_size = n())

# Count is just wrapping together group_by + summarize + n() to get ocunts of observations
penguins %>% count(species, island, sex)
```
